```{r}
#rm(list=ls(all = TRUE))
library(faraway)

library(stringr)
library(foreach)
library(ggplot2)
library(grid)
library(gridExtra)
library(plotrix)
library(nlme)
library(lme4)
library(car)
library(AICcmodavg)
library(lsmeans)
library(reshape2)
library(MASS)
library(sjPlot) #for plot_new
library(tidyverse)

source('Functions.R')

####### Input files ##########

setwd("./data/")

Instars <- read.csv(file = "GrasshopperData_3rdToAdult_SPR16.csv", header = TRUE, stringsAsFactors = FALSE)
str(Instars)

Instars$sex <- ifelse(Instars$sex == "", NA, Instars$sex)

##### Format dates and calculate ages ########

Instars$Date1_Hatch <- as.Date(Instars$Date_Hatch, format = "%m/%d/%Y")
Instars$Date1_1st <- as.Date(Instars$Date_1st, format = "%m/%d/%Y")
Instars$Date1_2nd <- as.Date(Instars$Date_2nd, format = "%m/%d/%Y")
Instars$Date1_3rd <- as.Date(Instars$Date_3rd, format = "%m/%d/%Y")
Instars$Date1_4th <- as.Date(Instars$Date_4th, format = "%m/%d/%Y")
Instars$Date1_5th <- as.Date(Instars$Date_5th, format = "%m/%d/%Y")
Instars$Date1_5th. <- as.Date(Instars$Date_5th., format = "%m/%d/%Y")
Instars$Date1_Adult <- as.Date(Instars$Date_Adult, format = "%m/%d/%Y")
Instars$Date1_Death <- as.Date(Instars$Date_Death, format = "%m/%d/%Y")

Instars$Age_3rd <- Instars$Date1_3rd - Instars$Date1_Hatch
Instars$Age_4th <- Instars$Date1_4th - Instars$Date1_Hatch
Instars$Age_5th <- Instars$Date1_5th - Instars$Date1_Hatch
Instars$Age_Adult <- Instars$Date1_Adult - Instars$Date1_Hatch


#trim out pell data

Instars <- Instars[Instars$Species == "dodg",]

```


```{r}
##### Plot time to adulthood ######

#plot based on individual means
MinSE <- function(x) {mean(x, na.rm = TRUE) - std.error(x, na.rm = TRUE)}
MaxSE <- function(x) {mean(x, na.rm = TRUE) + std.error(x, na.rm = TRUE)}

Give.N <- function(x){
  return(c(y = MaxSE(x)*1.01, label = length(x))) 
}

ggplot(data = Instars, aes(x = Site, y = Age_Adult, shape = sex, linetype = sex)) +
  rory_theme +
  facet_wrap(~Temp+Light, nrow = 1) +
  stat_summary(fun.y = mean, fun.ymin = MinSE, fun.ymax = MaxSE, na.rm = TRUE, size = 1.5, position = position_dodge(width = .6)) +
  stat_summary(aes(x = as.numeric(as.factor(Site))), fun.y = mean, geom = "line", size = 1.5, position = position_dodge(width = .6)) +
  #stat_summary(fun.data = Give.N, geom = "text", fun.y = median, position = position_dodge(width = .6), size = 7) +
  ylab("Time to adult (d)") + xlab("Site")
```


```{r}

######### Initial analysis ##################

#set factors

Instars$Site <- as.factor(Instars$Site)
Instars$sex <- as.factor(Instars$sex)
Instars$Temp <- as.factor(Instars$Temp)
Instars$Light <- as.factor(Instars$Light)
Instars$Female <- as.factor(Instars$Female)
Instars$Female2 <- as.factor(paste(Instars$Female, Instars$Site, sep = "_")) #this gives each mother her own ID (now differentiating between FY1's across sites)

hist(as.numeric(Instars$Age_Adult)) #not quite normal, should probably use a Poisson distribution...

#note: (1|Female2) means to count this as a random effect

Lmer0 <- glmer(as.numeric(Age_Adult) ~ sex * Site * Temp * Light + 
                 (1|Female2), family = poisson, na.action = 'na.omit', data = Instars)

Lmer1 <- glmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 sex:Site + sex:Temp + sex:Light + Site:Temp + Site:Light + Temp:Light + 
                 Site:Light:Temp +
                 (1|Female2), family = poisson, na.action = 'na.omit', data = Instars)

Lmer2 <- glmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 sex:Site + sex:Temp + sex:Light + Site:Temp + Site:Light + Temp:Light + 
                 (1|Female2), family = poisson, na.action = 'na.omit', data = Instars)

Lmer3 <- glmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                 (1|Female2), family = poisson, na.action = 'na.omit', data = Instars)

Lmer4 <- glmer(as.numeric(Age_Adult) ~ Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                 (1|Female2), family = poisson, na.action = 'na.omit', data = Instars)

Lmer5 <- glmer(as.numeric(Age_Adult) ~ Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light +
                 (1|Female2), family = poisson, na.action = 'na.omit', data = Instars)

aictab(list(Lmer0, Lmer1, Lmer2, Lmer3, Lmer4, Lmer5), modnames = c("Lmer0", "Lmer1", "Lmer2", "Lmer3", "Lmer4", "Lmer5"))
#Lmer3 is by far the preferred model according to AICc

summary(Lmer3)
Anova(Lmer3, type = 3)
Validate(Lmer3) #looks great
#Julia: need to read about the lsmeans function
#look at individual contrasts
lsmeans(Lmer3, pairwise ~ Site|Temp+Light) #A1 and C1 differ from one another in HV_S, LV_L, and LV_S
lsmeans(Lmer3, pairwise ~ Light|Temp) #Light generally has an effect in LV but not HV
lsmeans(Lmer3, pairwise ~ Temp|Light+Site) #Temp regime had an effect under every light and site, with LV always greater than HV

#plot lsmeans
Obj1<-data.frame(summary(lsmeans(Lmer3, ~ sex*Site*Temp*Light, type = "response")))

ggplot(data = Obj1, aes(y = response, x = Site, shape = sex, linetype = sex)) +
  rory_theme +
  facet_wrap(~Temp+Light, nrow = 1) +
  geom_errorbar(aes(ymax = asymp.UCL, ymin = asymp.LCL), position = position_dodge(width = .6)) +
  geom_line(aes(x = as.numeric(as.factor(Site))), size = 1.5, position = position_dodge(width = .6)) +
  geom_point(size = 6, position = position_dodge(width = .6)) +
  ylab("Time to adult (d, LS-means)") + xlab("Site")



```

```{r}
#check lmer for singularity, no singularity with lmer, OK to assume normal?
#NOTE: I rename it nLmer3 to distinguish from the original Lmer3. -Julia
nLmer3 <- lmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                 (1|Female2), na.action = 'na.omit', data = Instars)


#plot predictions
plot_model(nLmer3, type="pred", terms=c("Site","Temp","Light"), show.data=TRUE)
```


```{r}
Instars %>% group_by(sex, Site, Temp, Light) %>% summarize(num_obs=n(),num_mothers=n_distinct(Female2)) %>% ungroup()
```

```{r}
ex_cond <- Instars %>% filter(sex=="F" & Site=="B1" & Temp=="HV" & Light=="L")
print(ex_cond$Female2)
#so there's some redundancy in mothers within a set of conditions
```

```{r}
Instars %>% group_by(Female2) %>% summarize(num_conds=n_distinct(Temp, Light)) %>% ungroup()
#mothers are usually nested within a condition (so individuals in different combinations of Temp and Light don't typically have the same mother)
#however there are a few cases when a mother can be found in 2 or 3 conditions (i.e. F38_B1)
Instars %>% filter(Female2=="F38_B1") %>% group_by(Temp, Light) %>% summarize(n=n()) %>% ungroup()
```
QUESTION FOR LAUREN: It seems that neither case is met, but for future reference, which situation would mean that we didn't need to count mother as a random effect?
-Individuals from the same mother do not occur in the same combination of conditions
-Individuals from the same mother only occur in the same combination of conditions (do not occur across conditions)
My understanding from the last meeting was that the issue would be if we had females contributing multiple eggs to a treatment. And that one way we could address this issue is by averaging those. And then we wouldn't have the singularity. Just to check, is this correct?


Exploring gaussian... here I retest the different model and see which has the best AICc. It is no longer model 3. It is now the most complex model: model 0. Was I right to retest or is there an issue? See the error/warning below!
```{r}
nLmer0 <- lmer(as.numeric(Age_Adult) ~ sex * Site * Temp * Light + 
                 (1|Female2), na.action = 'na.omit', data = Instars)

nLmer1 <- lmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 sex:Site + sex:Temp + sex:Light + Site:Temp + Site:Light + Temp:Light + 
                 Site:Light:Temp +
                 (1|Female2), na.action = 'na.omit', data = Instars)

nLmer2 <- lmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 sex:Site + sex:Temp + sex:Light + Site:Temp + Site:Light + Temp:Light + 
                 (1|Female2), na.action = 'na.omit', data = Instars)

nLmer3 <- lmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                 (1|Female2), na.action = 'na.omit', data = Instars)

nLmer4 <- lmer(as.numeric(Age_Adult) ~ Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                 (1|Female2), na.action = 'na.omit', data = Instars)

nLmer5 <- lmer(as.numeric(Age_Adult) ~ Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light +
                 (1|Female2), na.action = 'na.omit', data = Instars)

aictab(list(nLmer0, nLmer1, nLmer2, nLmer3, nLmer4, nLmer5), modnames = c("nLmer0", "nLmer1", "nLmer2", "nLmer3", "nLmer4", "nLmer5"))

#nLmer0 is by far the preferred model according to AICc. It has all the weight. Is that suspicious / does it mean something's wrong?

#what does the error mean?:
# Model selection for fixed effects is only appropriate with ML estimation:
# REML (default) should only be used to select random effects for a constant set of fixed effects
```

Now trying it with ML (so REML=FALSE for each lmer call)
```{r}
nLmer0 <- lmer(as.numeric(Age_Adult) ~ sex * Site * Temp * Light + 
                 (1|Female2), na.action = 'na.omit', REML=FALSE, data = Instars)

nLmer1 <- lmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 sex:Site + sex:Temp + sex:Light + Site:Temp + Site:Light + Temp:Light + 
                 Site:Light:Temp +
                 (1|Female2), na.action = 'na.omit', REML=FALSE, data = Instars)

nLmer2 <- lmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 sex:Site + sex:Temp + sex:Light + Site:Temp + Site:Light + Temp:Light + 
                 (1|Female2), na.action = 'na.omit', REML=FALSE, data = Instars)

nLmer3 <- lmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                 (1|Female2), na.action = 'na.omit', REML=FALSE, data = Instars)

nLmer4 <- lmer(as.numeric(Age_Adult) ~ Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                 (1|Female2), na.action = 'na.omit', REML=FALSE, data = Instars)

nLmer5 <- lmer(as.numeric(Age_Adult) ~ Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light +
                 (1|Female2), na.action = 'na.omit', REML=FALSE, data = Instars)

aictab(list(nLmer0, nLmer1, nLmer2, nLmer3, nLmer4, nLmer5), modnames = c("nLmer0", "nLmer1", "nLmer2", "nLmer3", "nLmer4", "nLmer5"))

#interesting... it still has me select nLmer0.
```

NEW: Further exploring nLmer0
```{r}
summary(nLmer0)
Anova(nLmer0, type = 3)
Validate(nLmer0)
```

```{r}
#look at individual contrasts
lsmeans(nLmer0, pairwise ~ Site|Temp+Light) #A is significantly different from B and C at LV_L and HV_S; at LV_S it's just significantly different from C
lsmeans(nLmer0, pairwise ~ Light|Temp) #Light generally has an effect in LV but not HV
lsmeans(nLmer0, pairwise ~ Temp|Light+Site) #Temp regime had an effect under every light and site, with LV always greater than HV
```

```{r}
#crPlot(nLmer0, "Site) #ISSUE: doesn't like lmer class
```


Note: not sure about this code (below), actually. I found it online and should figure out exactly how it's working.
```{r}
d <- Instars %>% select(Age_Adult, sex, Site, Temp, Light) %>% drop_na()

# Fit the model
#fit <- lm(Sepal.Width ~ ., data = iris)

# Obtain predicted and residual values
d$predicted <- predict(nLmer0) 
d$residuals <- residuals(nLmer0) 

# Create plot
d %>% 
  gather(key = "iv", value = "x", -Age_Adult, -predicted, -residuals) %>%
  ggplot(aes(x = x, y = Age_Adult)) +
  geom_segment(aes(xend = x, yend = predicted), alpha = .2) +
  geom_point(aes(color = residuals)) +
  scale_color_gradient2(low = "blue", mid = "white", high = "red") +
  guides(color = FALSE) +
  geom_point(aes(y = predicted), shape = 1) +
  facet_grid(~ iv, scales = "free_x") +
  theme_bw()
```
```{r}
plot_model(Lmer0, type="pred", terms=c("Site","Temp","Light", "sex"), show.data=TRUE)
```




```{r}
d <- Instars %>% select(Age_Adult, sex, Site, Temp, Light, Female2) %>% drop_na() #dropped all NAs in advance to deal na.omit / na.fail issues
dat <- Instars
fm1 <- lmer(as.numeric(Age_Adult) ~ sex * Site * Temp * Light + 
                 (1|Female2), REML=FALSE, data = d)
dd <- dredge(fm1)
subset(dd, delta < 4)

#dredge says the best model is the most complex
```


END OF NEW

For curiousity: What happens when we compare models from poisson and gaussian? This code doesn't work bc "Functions do not support mixture of model classes"
```{r}
# aictab(list(nLmer0, nLmer1, nLmer2, nLmer3, nLmer4, nLmer5, Lmer0, Lmer1, Lmer2, Lmer3, Lmer4, Lmer5), modnames = c("nLmer0", "nLmer1", "nLmer2", "nLmer3", "nLmer4", "nLmer5", "Lmer0", "Lmer1", "Lmer2", "Lmer3", "Lmer4", "Lmer5"))
```

Exploring current Lmer3 (poisson) more 
Same code
```{r}
summary(Lmer3)
Anova(Lmer3, type = 3)
Validate(Lmer3) #looks great
#Julia: need to read about the lsmeans function
#look at individual contrasts
lsmeans(Lmer3, pairwise ~ Site|Temp+Light) #A1 and C1 differ from one another in HV_S, LV_L, and LV_S
lsmeans(Lmer3, pairwise ~ Light|Temp) #Light generally has an effect in LV but not HV
lsmeans(Lmer3, pairwise ~ Temp|Light+Site) #Temp regime had an effect under every light and site, with LV always greater than HV

#plot lsmeans
Obj1<-data.frame(summary(lsmeans(Lmer3, ~ sex*Site*Temp*Light, type = "response")))

ggplot(data = Obj1, aes(y = response, x = Site, shape = sex, linetype = sex)) +
  rory_theme +
  facet_wrap(~Temp+Light, nrow = 1) +
  geom_errorbar(aes(ymax = asymp.UCL, ymin = asymp.LCL), position = position_dodge(width = .6)) +
  geom_line(aes(x = as.numeric(as.factor(Site))), size = 1.5, position = position_dodge(width = .6)) +
  geom_point(size = 6, position = position_dodge(width = .6)) +
  ylab("Time to adult (d, LS-means)") + xlab("Site")


#check lmer for singularity, no singularity with lmer, OK to assume normal?
Lmer3 <- lmer(as.numeric(Age_Adult) ~ sex + Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                 (1|Female2), na.action = 'na.omit', data = Instars)


#plot predictions
plot_model(Lmer3, type="pred", terms=c("Site","Temp","Light"), show.data=TRUE)
```



```{r}
Anova(nLmer0, type = 3)
```
```{r}
Anova(Lmer0, type = 3)
```

```{r}
coefficients(Lmer3)
```

