---
title: "Q10_w_data"
output: html_notebook
---

#Set up

Set working directory to source file location
```{r setup}
knitr::opts_knit$set(root.dir = './')
```

Load packages and functions
```{r, echo=FALSE, warning=FALSE, message=FALSE}
# Initial
rm(list=ls(all = TRUE))
library(stringr)
library(foreach)
library(ggplot2)
library(grid)
library(gridExtra)
library(plotrix)
library(nlme)
library(lme4)
library(car)
library(AICcmodavg)
library(lsmeans)
library(reshape2)
library(MASS)
library(nls2)
library(tidyverse)
library(kableExtra)
library(faraway)
library(sjPlot) #for plot_new
library(tidyverse)
library(knitr)
library(afex)
library(RColorBrewer)
library(ggeffects)
library(cowplot)
library(stringr)

#webshot::install_phantomjs()
library(kableExtra)
library(nlme)

source('Functions.R')

```

Functions and labels
```{r}


# New facet label names for supp variable
Photoperiod.labs <- c("Long photoperiod", "Short photoperiod")
names(Photoperiod.labs) <- c("L", "S")
 
#Temperature.labs <- c("High var", "Low var")
#names(Temperature.labs) <- c("HV", "LV")
##decided to stick with HV and LB

#plot based on individual means
MinSE <- function(x) {mean(x, na.rm = TRUE) - std.error(x, na.rm = TRUE)}
MaxSE <- function(x) {mean(x, na.rm = TRUE) + std.error(x, na.rm = TRUE)}

Give.N <- function(x){
  return(c(y = MaxSE(x)*1.01, label = length(x))) 
}
```

Growth and development data
```{r}
# Instars from GrowthRate_Script_2016.R
Instars <- read.csv(file = "data/GrasshopperData_3rdToAdult_SPR16.csv", header = TRUE, stringsAsFactors = FALSE)
#str(Instars)
Instars$sex <- ifelse(Instars$sex == "", NA, Instars$sex)

#Format dates and calculate ages
Instars$Date1_Hatch <- as.Date(Instars$Date_Hatch, format = "%m/%d/%Y")
Instars$Date1_1st <- as.Date(Instars$Date_1st, format = "%m/%d/%Y")
Instars$Date1_2nd <- as.Date(Instars$Date_2nd, format = "%m/%d/%Y")
Instars$Date1_3rd <- as.Date(Instars$Date_3rd, format = "%m/%d/%Y")
Instars$Date1_4th <- as.Date(Instars$Date_4th, format = "%m/%d/%Y")
Instars$Date1_5th <- as.Date(Instars$Date_5th, format = "%m/%d/%Y")
Instars$Date1_5th. <- as.Date(Instars$Date_5th., format = "%m/%d/%Y")
Instars$Date1_Adult <- as.Date(Instars$Date_Adult, format = "%m/%d/%Y")
Instars$Date1_Death <- as.Date(Instars$Date_Death, format = "%m/%d/%Y")

Instars$Age_3rd <- Instars$Date1_3rd - Instars$Date1_Hatch
Instars$Age_4th <- Instars$Date1_4th - Instars$Date1_Hatch
Instars$Age_5th <- Instars$Date1_5th - Instars$Date1_Hatch
Instars$Age_Adult <- Instars$Date1_Adult - Instars$Date1_Hatch

#trim out pell data
Instars <- Instars[Instars$Species == "dodg",]

#set factors
Instars$Site <- as.factor(Instars$Site)
Instars$sex <- as.factor(Instars$sex)
Instars$Temp <- as.factor(Instars$Temp)
Instars$Light <- as.factor(Instars$Light)
Instars$Female <- as.factor(Instars$Female)
Instars$Female2 <- as.factor(paste(Instars$Female, Instars$Site, sep = "_")) 
  #Female2 gives each mother her own ID (differentiates between FY1's across sites)
Instars= Instars[which(Instars$sex %in% c("F","M")),] #ADDING THIS HERE -- I think we do this in effect anyway

Instars_names <- Instars %>% rename(Sex=sex, Temperature=Temp, Photoperiod=Light)
Instars_names$Site <- recode(Instars_names$Site, A1 = "2195m", B1="2591m", C1="3048m")
Instars_names$Sex <- recode(Instars_names$Sex, M = "Male", F="Female")

#For devinstelopment by instar
D_Instars_Adult <- Instars_names[is.na(Instars_names$Age_Adult) == FALSE,]
D_Instars_Adult_Long <- melt(D_Instars_Adult[,c(1:8,50:54)], id.vars = c("Individual", "CCode", "Female", "Female2", "Site", "Species", "Sex", "Temperature", "Photoperiod")) 
#Make instar numeric
D_Instars_Adult_Long$Instar=3
D_Instars_Adult_Long$Instar[D_Instars_Adult_Long$variable=="Age_4th"]=4
D_Instars_Adult_Long$Instar[D_Instars_Adult_Long$variable=="Age_5th"]=5
D_Instars_Adult_Long$Instar[D_Instars_Adult_Long$variable=="Age_Adult"]=6

#For mass by instar
M_Instars_Adult <- Instars_names[is.na(Instars_names$Mass_Adult) == FALSE,]
M_Instars_Adult_Long <-  melt(M_Instars_Adult[,c(1:8,18,21,24,30,54)], id.vars = c("Individual", "CCode", "Female", "Female2", "Site", "Species", "Sex", "Temperature", "Photoperiod")) #tracks the mass (value) when each individual reached each instar (variable)
#Make instar numeric
M_Instars_Adult_Long$Instar=3
M_Instars_Adult_Long$Instar[M_Instars_Adult_Long$variable=="Mass_4th"]=4
M_Instars_Adult_Long$Instar[M_Instars_Adult_Long$variable=="Mass_5th"]=5
M_Instars_Adult_Long$Instar[M_Instars_Adult_Long$variable=="Mass_Adult"]=6



```


General thoughts:
We treat Q10 as if it could vary at different sites. Could R1 also (R at T=24) be different for different sites (through evolution)? 

And how does sex factor in? Do we have a different number of energetic units that needs to be reached? Different R1 and/or Q10? We could just choose a sex and ignore this Q.

Fitting curves:
Our parameters are R1[site], Q10[site]... should there be some constant somewhere in here (maybe the 1000)?

days.dev=function(Q10, T2l=22, T2h=26, T1=24, Pd=12, Pl=24-Pd)  1/(Pd/1000*Q10^((T2l-T1)/10)+ Pl/1000*Q10^((T2h-T1)/10))

So what are our data? age_adult 

Could we deduce # of energy units to arrive at each instar (maybe from all the data) and then use time to each instar as data? Is this advisable? [Keep it at time to adult for now!]

Also, do we have past data from which we can deduce R1 for each site? Maybe from when they were reared at constant temperatures?

So far I haven't gotten into growth -- just development. Are we assuming something about the relationship between G & D right now? Does the function you provided in Q10 account for growth leveling off? Is "days" the number of days it takes to reach adulthood (and then the output is adult mass) Or is it supposed to predict mass for any number of days?

Possibly useful source... could incorporate random effects (Female2), but not sure how much it matters
https://stackoverflow.com/questions/55778838/how-to-fit-a-nls-model-with-mixed-effects

```{r}
dev.dat <- Instars_names %>% select(Site, Sex, Temperature, Photoperiod, Female2, Age_Adult)
```



```{r}
days.dev=function(Q10, R1, Tvar){ #fitting Q10 and R1
  num_days <- 1/(12/1000*(Q10^((Tvar)/10)+ Q10^((-Tvar)/10)))
  return(num_days)
} 
```

Source: https://stats.stackexchange.com/questions/171154/fitting-known-equation-to-data/171191 
```{r}
fs <- dev.dat %>% filter(Sex=="Female") %>% select(-Female2)


dat3048 <- fs %>% filter(Site=="3048m") %>% filter(!is.na(Age_Adult))
dat3048 <- dat3048 %>% mutate(Tvar=ifelse(Temperature=="HV", 4, 2)) 
fit3048 <- gnls(Age_Adult ~ days.dev(Q10, 1, Tvar), data=dat3048, start=list(Q10=1.75))
dat3048_c <- cbind(dat3048, fit3048$fitted) %>% rename(fit=`fit3048$fitted`)

dat2591 <- fs %>% filter(Site=="2591m") %>% filter(!is.na(Age_Adult))
dat2591 <- dat2591 %>% mutate(Tvar=ifelse(Temperature=="HV", 4, 2)) 
fit2591 <- gnls(Age_Adult ~ days.dev(Q10, 1, Tvar), data=dat2591, start=list(Q10=1.75)) 
dat2591_c <- cbind(dat2591, fit2591$fitted) %>% rename(fit=`fit2591$fitted`)

dat2195 <- fs %>% filter(Site=="2195m") %>% filter(!is.na(Age_Adult))
dat2195 <- dat2195 %>% mutate(Tvar=ifelse(Temperature=="HV", 4, 2)) 
fit2195 <- gnls(Age_Adult ~ days.dev(Q10, 1, Tvar), data=dat2195, start=list(Q10=1.75)) 
dat2195_c <- cbind(dat2195, fit2195$fitted) %>% rename(fit=`fit2195$fitted`)
```

Trying to plot them together
```{r}
all_f <- rbind(dat3048_c,dat2591_c,dat2195_c)

ggplot(data = all_f, aes(x =Temperature)) + facet_grid(.~Site) + geom_point(aes(y = Age_Adult, color="Age_Adult")) + geom_point(aes(y=fit, color="fit"))
```
```{r}
days.hv=sapply(seq(0.6,5,0.1), FUN="days.dev", Tvar=4) 
plot(seq(0.6,5,0.1), days.hv, type="l", col="red", xlab="Q10", ylab="Predicted days to adult")


days.lv=sapply(seq(0.6,5,0.1), FUN="days.dev", Tvar=2)
points(seq(0.6,5,0.1), days.lv, type="l", col="blue")

abline(v=as.numeric(fit2195$coefficients)) #2195
text(as.numeric(fit2195$coefficients)-.25, 34.5, "2195m")
abline(v=as.numeric(fit2591$coefficients)) #2951
text(as.numeric(fit2591$coefficients)-.25, 34.5, "2951m")
abline(v=as.numeric(fit3048$coefficients)) #3048
text(as.numeric(fit3048$coefficients)-.25, 34.5, "3048m")

#could put color coded data points here if it would be helpful

```

## Now males

```{r}
ms <- dev.dat %>% filter(Sex=="Male") %>% select(-Female2)

dat3048 <- ms %>% filter(Site=="3048m") %>% filter(!is.na(Age_Adult))
dat3048 <- dat3048 %>% mutate(Tvar=ifelse(Temperature=="HV", 4, 2)) 
fit3048 <- gnls(Age_Adult ~ days.dev(Q10, 1, Tvar), data=dat3048, start=list(Q10=1.75))
dat3048_c <- cbind(dat3048, fit3048$fitted) %>% rename(fit=`fit3048$fitted`)

dat2591 <- ms %>% filter(Site=="2591m") %>% filter(!is.na(Age_Adult))
dat2591 <- dat2591 %>% mutate(Tvar=ifelse(Temperature=="HV", 4, 2)) 
fit2591 <- gnls(Age_Adult ~ days.dev(Q10, 1, Tvar), data=dat2591, start=list(Q10=1.75)) 
dat2591_c <- cbind(dat2591, fit2591$fitted) %>% rename(fit=`fit2591$fitted`)

dat2195 <- ms %>% filter(Site=="2195m") %>% filter(!is.na(Age_Adult))
dat2195 <- dat2195 %>% mutate(Tvar=ifelse(Temperature=="HV", 4, 2)) 
fit2195 <- gnls(Age_Adult ~ days.dev(Q10, 1, Tvar), data=dat2195, start=list(Q10=1.75)) 
dat2195_c <- cbind(dat2195, fit2195$fitted) %>% rename(fit=`fit2195$fitted`)
```

Trying to plot them together
```{r}
all_m <- rbind(dat3048_c,dat2591_c,dat2195_c)

ggplot(data = all_m, aes(x =Temperature)) + facet_grid(.~Site) + geom_point(aes(y = Age_Adult, color="Age_Adult")) + geom_point(aes(y=fit, color="fit"))
```

```{r}
days.hv=sapply(seq(0.6,5,0.1), FUN="days.dev", Tvar=4) 
plot(seq(0.6,5,0.1), days.hv, type="l", col="red", xlab="Q10", ylab="Predicted days to adult")


days.lv=sapply(seq(0.6,5.2,0.1), FUN="days.dev", Tvar=2)
points(seq(0.6,5.2,0.1), days.lv, type="l", col="blue")

abline(v=as.numeric(fit2195$coefficients)) #2195
text(as.numeric(fit2195$coefficients)-.25, 34.5, "2195m")
abline(v=as.numeric(fit2591$coefficients)) #2951
text(as.numeric(fit2591$coefficients)+.25, 34.5, "2951m")
abline(v=as.numeric(fit3048$coefficients)) #3048
text(as.numeric(fit3048$coefficients)-.25, 34.5, "3048m")

#could put color coded data points here if it would be helpful
```

