---
title: "Results_manuscript_draft"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
library(faraway)
library(stringr)
library(foreach)
library(ggplot2)
library(grid)
library(gridExtra)
library(plotrix)
library(nlme)
library(lme4)
library(car)
library(AICcmodavg)
library(lsmeans)
library(reshape2)
library(MASS)
library(sjPlot) #for plot_new
library(tidyverse)
library(knitr)

source('Functions.R')

####### Input files ##########

#setwd("./data/")

Instars <- read.csv(file = "./data/GrasshopperData_3rdToAdult_SPR16.csv", header = TRUE, stringsAsFactors = FALSE)
str(Instars)


Instars$sex <- ifelse(Instars$sex == "", NA, Instars$sex)

##### Format dates and calculate ages ########

Instars$Date1_Hatch <- as.Date(Instars$Date_Hatch, format = "%m/%d/%Y")
Instars$Date1_1st <- as.Date(Instars$Date_1st, format = "%m/%d/%Y")
Instars$Date1_2nd <- as.Date(Instars$Date_2nd, format = "%m/%d/%Y")
Instars$Date1_3rd <- as.Date(Instars$Date_3rd, format = "%m/%d/%Y")
Instars$Date1_4th <- as.Date(Instars$Date_4th, format = "%m/%d/%Y")
Instars$Date1_5th <- as.Date(Instars$Date_5th, format = "%m/%d/%Y")
Instars$Date1_5th. <- as.Date(Instars$Date_5th., format = "%m/%d/%Y")
Instars$Date1_Adult <- as.Date(Instars$Date_Adult, format = "%m/%d/%Y")
Instars$Date1_Death <- as.Date(Instars$Date_Death, format = "%m/%d/%Y")

Instars$Age_3rd <- Instars$Date1_3rd - Instars$Date1_Hatch
Instars$Age_4th <- Instars$Date1_4th - Instars$Date1_Hatch
Instars$Age_5th <- Instars$Date1_5th - Instars$Date1_Hatch
Instars$Age_Adult <- Instars$Date1_Adult - Instars$Date1_Hatch


#trim out pell data

Instars <- Instars[Instars$Species == "dodg",]


#set factors

Instars$Site <- as.factor(Instars$Site)
Instars$sex <- as.factor(Instars$sex)
Instars$Temp <- as.factor(Instars$Temp)
Instars$Light <- as.factor(Instars$Light)
Instars$Female <- as.factor(Instars$Female)
Instars$Female2 <- as.factor(paste(Instars$Female, Instars$Site, sep = "_")) #this gives each mother her own ID (now differentiating between FY1's across sites)
```

## Results
### Maturation Rate

Examine age to adult with no consideration of time to earlier instars

For analyses, I used the glmer function from Lme4 library to model the effects of sex, site, temp regime, and light regime on age of adulthood, assuming a normal distribution.  I included the identity of the grasshopper's mother as a random effect.  I constructed 6 nested models: 1) including all interactions, 2) dropped 3- and 4-way interactions with sex, 3) only 2-way interactions, 4) all interactions not including sex, 5) sex removed completely, 6) sex and 3-way interaction removed completely.  The preferred model (ΔAICc > 10) is the model including the main effects of all 4 varaiables, as well as all of their higher order interactions.  

Plot based on individual means:
```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.dim=c(9,7)}

# New facet label names for sex variable
sex.labs <- c("Female", "Male")
names(sex.labs) <- c("F", "M")

# New facet label names for supp variable
Light.labs <- c("Long daylight", "Short daylight")
names(Light.labs) <- c("L", "S")
# 
# Temp.labs <- c("High var", "Low var")
# names(Temp.labs) <- c("HV", "LV")

#plot based on individual means
MinSE <- function(x) {mean(x, na.rm = TRUE) - std.error(x, na.rm = TRUE)}
MaxSE <- function(x) {mean(x, na.rm = TRUE) + std.error(x, na.rm = TRUE)}

Give.N <- function(x){
  return(c(y = MaxSE(x)*1.01, label = length(x))) 
}

#drop NA sex
Instars= Instars[which(Instars$sex %in% c("F","M")),]

ggplot(data = Instars, aes(x = Site, y = Age_Adult, color = Temp)) +
#  rory_theme +
  facet_grid(sex~Light, labeller=labeller(sex = sex.labs, Light = Light.labs)) +
  stat_summary(fun.y = mean, fun.ymin = MinSE, fun.ymax = MaxSE, na.rm = TRUE, size = .5, position = position_dodge(width = .3)) +
  stat_summary(aes(x = as.numeric(as.factor(Site))), fun.y = mean, geom = "line", size = .5, position = position_dodge(width = .3)) +
  #stat_summary(fun.data = Give.N, geom = "text", fun.y = median, position = position_dodge(width = .6), size = 7) +
  ylab("Time to adult (d)") + xlab("Site")+scale_color_manual(name="Temp var", labels=c("High var", "Low var"), values = c("#D6604D", "#4393C3")) + scale_x_discrete(labels=c("2195m", "2591m", "3048m"))+ theme(axis.text.x = element_text(angle = 90, vjust = .2, hjust=1))
```


Here is an ANOVA table: 
```{r, echo=FALSE}
library(afex)

#webshot::install_phantomjs()
library(kableExtra)

Instars_names <- Instars %>% mutate(Sex=sex, Tempvar=Temp, Daylength=Light)

Instars_names$Site <- recode(Instars_names$Site, A1 = "2195m", B1="2591m", C1="3048m")


nLmer0 <- lmer(as.numeric(Age_Adult) ~ Sex * Site * Tempvar * Daylength +
                 (1|Female2), na.action = 'na.omit', REML=FALSE, data = Instars_names)


a <- Anova(nLmer0, type=3)
a$Significance <- "   "
a$Significance[a$`Pr(>Chisq)`<.05] <- "*  "
a$Significance[a$`Pr(>Chisq)`<.001] <- "***"
a$`Pr(>Chisq)` <- format(a$`Pr(>Chisq)`, scientific=TRUE, digits=3)
a$`Pr(>Chisq)` <- as.character(a$`Pr(>Chisq)`)
a <- a %>% unite(p, c(`Pr(>Chisq)`, Significance), sep="")
options(knitr.kable.NA = '')
kable(a, digits=3, col.names=c("<var>&chi;<sup>2</sup></var>", "df", "p"), escape=FALSE, format="html") %>% kable_styling() #%>% save_kable("adultanova.png")

```


```{r}

s<- summary(nLmer0)
kable(s[["coefficients"]], digits=3, format="html") %>% kable_styling() #%>% save_kable("adultsummary2.png")
```
The significant main effects were that grasshoppers developed faster at high temperature variance (p<.001) and long photoperiod (p<.05) and that males developed faster than females (p<.05). Site alone did not have a significant effect according to our model, but the highest elevation site (C1) did appear to develop faster except for female grasshoppers in a long photoperiod environment. There was also an interaction between day length and light variance where long days actually delayed development for grasshoppers in low temperature variance environments. Long days sped up development for males in environments with high temperature variance, but not for females in those environments.

Analyzing instars
```{r}
Instars_Adult <- Instars[is.na(Instars$Age_Adult) == FALSE,]
Instars_Adult_Long <- melt(Instars_Adult[,c(1:8,50:54)], id.vars = c("Individual", "CCode", "Female", "Female2", "Site", "Species", "sex", "Temp", "Light")) #tracks the time (value) when each individual reached each instar (variable)

#I changed the nesting from what Rory had ((1|Individual/variable/Female2)). lmer gave me an error with that nesting. I referred to this source (particularly this example: leafLength ~ treatment + (1|Bed/Plant/Leaf) + (1|Season)) , but I'm not entirely sure that I'm right.

Lmer0.1 <- lmer(as.numeric(value) ~ sex * Site * Temp * Light + 
                   (1|Female2/Individual)+ (1|variable), na.action = 'na.omit', REML=FALSE, data = Instars_Adult_Long) 

Lmer1.1 <- lmer(as.numeric(value) ~ sex + Site + Temp + Light + 
                   sex:Site + sex:Temp + sex:Light + Site:Temp + Site:Light + Temp:Light + 
                   Site:Light:Temp +
                   (1|Female2/Individual) + (1|variable), na.action = 'na.omit', REML=FALSE, data = Instars_Adult_Long)

Lmer2.1 <- lmer(as.numeric(value) ~ sex + Site + Temp + Light + 
                   sex:Site + sex:Temp + sex:Light + Site:Temp + Site:Light + Temp:Light + 
                   (1|Female2/Individual)+ (1|variable), na.action = 'na.omit', REML=FALSE, data = Instars_Adult_Long)

Lmer3.1 <- lmer(as.numeric(value) ~ sex + Site + Temp + Light + 
                   Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                   (1|Female2/Individual)+ (1|variable), na.action = 'na.omit', REML=FALSE, data = Instars_Adult_Long)

Lmer4.1 <- lmer(as.numeric(value) ~ Site + Temp + Light + 
                   Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                   (1|Female2/Individual)+ (1|variable), na.action = 'na.omit', REML=FALSE, data = Instars_Adult_Long)

Lmer5.1 <- lmer(as.numeric(value) ~ Site + Temp + Light + 
                   Site:Temp + Site:Light + Temp:Light +
                   (1|Female2/Individual)+ (1|variable), na.action = 'na.omit', REML=FALSE, data = Instars_Adult_Long)

aictab(list(Lmer0.1, Lmer1.1, Lmer2.1, Lmer3.1, Lmer4.1, Lmer5.1), modnames = c("Lmer0.1", "Lmer1.1", "Lmer2.1", "Lmer3.1", "Lmer4.1", "Lmer5.1"))
#I get 4.1 but it's quite close to other models. 0.1 (the most complex) is last! 4.1 is all combinations excluding sex (main effect and all interactions)

summary(Lmer4.1)
Anova(Lmer4.1)

```

```{r}
#plotting marginal effects

# 4 way interaction
plot_model(nLmer0, type="pred", terms=c("Sex", "Site", "Tempvar", "Daylength"), show.data=FALSE)

# main effects
plot_model(nLmer0, type="pred", terms=c("Sex"), show.data=FALSE)
plot_model(nLmer0, type="pred", terms=c("Tempvar"), show.data=FALSE)
plot_model(nLmer0, type="pred", terms=c("Daylength"), show.data=FALSE)
plot_model(nLmer0, type="pred", terms=c("Site"), show.data=FALSE) #not significant just taking a look

plot_model(nLmer0, type="pred", terms=c("Site", "Tempvar"), show.data=FALSE)
plot_model(nLmer0, type="pred", terms=c("Site", "Daylength"), show.data=FALSE)
plot_model(nLmer0, type="pred", terms=c("Sex", "Tempvar"), show.data=FALSE)
plot_model(nLmer0, type="pred", terms=c("Tempvar", "Daylength"), show.data=FALSE)
```


```{r, warning=FALSE, message=FALSE}
#silenced a warning... go back and check

levels(Instars_Adult_Long$variable) <- c("3rd", "4th", "5th", "Adult")
Temp.labs <- c("High temp var", "Low temp var")
names(Temp.labs) <- c("HV", "LV")

ggplot(data = Instars_Adult_Long, aes(x = variable, y = value, col = Site)) +
  facet_grid(Temp~sex+Light, labeller=labeller(Temp=Temp.labs, Light = Light.labs, sex=sex.labs)) +
  stat_summary(fun.y = mean, fun.ymin = MinSE, fun.ymax = MaxSE, na.rm = TRUE, size = .5, position = position_dodge(width = .3)) +
  stat_summary(aes(x = as.numeric(as.factor(variable))), fun.y = mean, geom = "line", size = .5, position = position_dodge(width = .3)) + scale_color_manual(labels=c("2195m", "2591m", "3048m"), values = brewer.pal(n = 8, name = "Blues")[c(8,6,4)]) +
  #stat_summary(fun.data = Give.N, geom = "text", fun.y = median, position = position_dodge(width = .6), size = 7) +
  ylab("Time (d)") + xlab("Instar")
```

Looking at mass
plot
```{r}
ggplot(data = Instars, aes(x = Site, y = as.numeric(Mass_Adult), color = Temp)) +
#  rory_theme +
  facet_grid(sex~Light, labeller=labeller(sex = sex.labs, Light = Light.labs)) +
  stat_summary(fun.y = mean, fun.ymin = MinSE, fun.ymax = MaxSE, na.rm = TRUE, size = .5, position = position_dodge(width = .3)) +
  stat_summary(aes(x = as.numeric(as.factor(Site))), fun.y = mean, geom = "line", size = .5, position = position_dodge(width = .3)) +
  #stat_summary(fun.data = Give.N, geom = "text", fun.y = median, position = position_dodge(width = .6), size = 7) +
  ylab("Mass as adult (g)") + xlab("Site")+scale_color_manual(name="Temp var", labels=c("High var", "Low var"), values = c("#D6604D", "#4393C3")) + scale_x_discrete(labels=c("2195m", "2591m", "3048m"))+ theme(axis.text.x = element_text(angle = 90, vjust = .2, hjust=1))


```

Analysis
```{r}
LmerM0 <- lmer(as.numeric(Mass_Adult) ~ sex * Site * Temp * Light + 
                 (1|Female2), 
               REML = FALSE,
               na.action = 'na.omit', data = Instars)

LmerM1 <- lmer(as.numeric(Mass_Adult) ~ sex + Site + Temp + Light + 
                 sex:Site + sex:Temp + sex:Light + Site:Temp + Site:Light + Temp:Light + 
                 Site:Light:Temp +
                 (1|Female2), 
               REML = FALSE, 
               na.action = 'na.omit', data = Instars) #boundary (singular) fit: see ?isSingular

LmerM2 <- lmer(as.numeric(Mass_Adult) ~ sex + Site + Temp + Light + 
                 sex:Site + sex:Temp + sex:Light + Site:Temp + Site:Light + Temp:Light + 
                 (1|Female2), 
               REML = FALSE,
               na.action = 'na.omit', data = Instars)

LmerM3 <- lmer(as.numeric(Mass_Adult) ~ sex + Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                 (1|Female2), 
               REML = FALSE,
               na.action = 'na.omit', data = Instars) #boundary (singular) fit: see ?isSingular

LmerM4 <- lmer(as.numeric(Mass_Adult) ~ Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light + Site:Temp:Light +
                 (1|Female2), 
               REML = FALSE, 
               na.action = 'na.omit', data = Instars) #boundary (singular) fit: see ?isSingular

LmerM5 <- lmer(as.numeric(Mass_Adult) ~ Site + Temp + Light + 
                 Site:Temp + Site:Light + Temp:Light +
                 (1|Female2), 
               REML = FALSE,
               na.action = 'na.omit', data = Instars) #boundary (singular) fit: see ?isSingular

aictab(list(LmerM0, LmerM1, LmerM2, LmerM3, LmerM4, LmerM5), modnames = c("LmerM0", "LmerM1", "LmerM2", "LmerM3", "LmerM4", "LmerM5"))

#M2 is preferred, followed closely by M3 and M1

```
Anova according to M0 [But I'm inclined to go with M2]
```{r}
a <- Anova(LmerM0, type=3)
a$Significance <- "   "
a$Significance[a$`Pr(>Chisq)`<.05] <- "*  "
a$Significance[a$`Pr(>Chisq)`<.001] <- "***"
a$`Pr(>Chisq)` <- format(a$`Pr(>Chisq)`, scientific=TRUE, digits=3)
a$`Pr(>Chisq)` <- as.character(a$`Pr(>Chisq)`)
a <- a %>% unite(p, c(`Pr(>Chisq)`, Significance), sep="")
options(knitr.kable.NA = '')
kable(a, digits=3, col.names=c("<var>&chi;<sup>2</sup></var>", "df", "p"), escape=FALSE, format="html") %>% kable_styling() #%>% save_kable("adultanova.png")
```

Summary according to M0
```{r}

```

Anova according to M2
```{r}
a <- Anova(LmerM2, type=3)
a$Significance <- "   "
a$Significance[a$`Pr(>Chisq)`<.05] <- "*  "
a$Significance[a$`Pr(>Chisq)`<.001] <- "***"
a$`Pr(>Chisq)` <- format(a$`Pr(>Chisq)`, scientific=TRUE, digits=3)
a$`Pr(>Chisq)` <- as.character(a$`Pr(>Chisq)`)
a <- a %>% unite(p, c(`Pr(>Chisq)`, Significance), sep="")
options(knitr.kable.NA = '')
kable(a, digits=3, col.names=c("<var>&chi;<sup>2</sup></var>", "df", "p"), escape=FALSE, format="html") %>% kable_styling() %>% save_kable("massanova.png")
```

Summary according to M2
```{r}
s <- summary(LmerM2)
kable(s[["coefficients"]], digits=3, format="html") %>% kable_styling() %>% save_kable("masssummary2.png")
```


```{r, warning=FALSE, message=FALSE}
#silenced a warning... go back and check

levels(Instars_Adult_Long$variable) <- c("3rd", "4th", "5th", "Adult")
Temp.labs <- c("High temp var", "Low temp var")
names(Temp.labs) <- c("HV", "LV")

ggplot(data = Instars_Adult_Long, aes(x = variable, y = value, col = Site)) +
  facet_grid(Temp~sex+Light, labeller=labeller(Temp=Temp.labs, Light = Light.labs, sex=sex.labs)) +
  stat_summary(fun.y = mean, fun.ymin = MinSE, fun.ymax = MaxSE, na.rm = TRUE, size = .5, position = position_dodge(width = .3)) +
  stat_summary(aes(x = as.numeric(as.factor(variable))), fun.y = mean, geom = "line", size = .5, position = position_dodge(width = .3)) + scale_color_manual(labels=c("2195m", "2591m", "3048m"), values = brewer.pal(n = 8, name = "Blues")[c(8,6,4)]) +
  #stat_summary(fun.data = Give.N, geom = "text", fun.y = median, position = position_dodge(width = .6), size = 7) +
  ylab("Time (d)") + xlab("Instar")
```

